---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Caitlyn Angley"
output: 
  html_document:
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse) #loading tidyverse
```

<br><br>

## Introduction
The data I chose is Women in the Workplace. I chose this data set because I have always been interested in the differences between men and women in the workplace, especially dealing with wages. This data set includes data about wages earned by men vs. women, what sectors they work in, as well as who is working part-time or full-time. 
[Link to the Data!](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-03-05)

```{r read-examine-data}
jobs_gender <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/jobs_gender.csv")
earnings_female <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/earnings_female.csv") 
employed_gender <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/employed_gender.csv") 

glimpse(earnings_female) #looking at each dataset
glimpse(employed_gender)
glimpse(jobs_gender)
```

<br><br>

## Question 1

#### How has female full-time employment changed over time?

### Methods
```{r question_1_methods}
employed_gender%>% #use employed gender part of data set
  ggplot()+ #use ggplot
  aes(x=year,
      y=full_time_female)+ #year on x, amount of females on y
  geom_line(color= "hotpink")+ #make a line plot with a pink line
  geom_point(color= "purple")+ #add purple points to the line
  theme_bw()+ #change the theme
  labs(x= "Year",
       y= "Females Working Full Time",
       title= "Amount of Females Working Full Time Over Time") #change the labels and add a title
```

### Answer

The amount of females working full time has gone up and down over the years, but ended up in generally the same spot.

<br><br>

## Question 2

#### How has female earnings in Life, Physical, and Social Science jobs changed over time?

### Methods
```{r question_2_methods}
jobs_gender%>% #using the jobs_gender tibble
  select(year, minor_category, workers_female)%>% #only want to look at these columns
  filter(minor_category== "Life, Physical, and Social Science")%>% #only want to see women in life physical and social science
  group_by(year)%>% #group by the year
  summarize(workers_female=sum(workers_female))%>% #find the amount of women for each year
  ggplot()+ #use ggplot
  aes(x=year,
      y= workers_female)+ #year on x, female workers on y
  geom_point()+ #have points on the plot
  geom_line(color= "purple")+ #make a line plot
  theme_minimal()+ #change the theme
  labs(x="Year",
       y="Workers Female",
       title= "Women Working in Life, Physical, and Social Science Over Time") #change labels and add a title

```
<br>

### Answer

The amount of women working in life, physical, and social science over time has increased since 2013. 

<br><br>

## Question 3

#### Do males make more money than woman as service workers?

### Methods

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### How has the amount of women biological scientists changed over the years?

### Methods

### Answer

Replace this text with your answer to your question.
