---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Caitlyn Angley"
output: 
  html_document:
    theme: cerulean
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction
The data I chose is Women in the Workplace. I chose this data set because I have always been interested in the differences between men and women in the workplace, especially dealing with wages. This data set includes data about wages earned by men vs. women, what sectors they work in, as well as who is working part-time or full-time. 
[Link to the Data!](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-03-05)

```{r read-examine-data}
jobs_gender <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/jobs_gender.csv")
earnings_female <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/earnings_female.csv") 
employed_gender <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/employed_gender.csv") 

glimpse(earnings_female)
glimpse(employed_gender)
glimpse(jobs_gender)
```

<br><br>

## Question 1

#### How has female full-time employment changed over time?

### Methods

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### How has female earnings in Life, Physical, and Social Science jobs changed over time?

### Methods

### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### Do males make more money than woman as service workers?.

### Methods

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### How has the amount of women biological scientists changed over the years?

### Methods

### Answer

Replace this text with your answer to your question.
